Gravitational-wave sensitivity curves

### 2014-07-04 noise_curve.tex
Section 2
Ending

\documentclass[fleqn,12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
\usepackage{iopams}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{natbib}
\usepackage{appendix}
\usepackage[margin=1cm]{caption}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{color}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 	definition of a solar mass symbol for use in equations.      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Msun}{\ensuremath{M_{ \odot }}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\cplb}[1]{{\color{red} #1}}
\newcommand{\rhc}[1]{{\color{green} #1}}
\newcommand{\cjm}[1]{{\color{blue} #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Concluding remarks}\label{sec:discussion}
When quantifying the sensitivity of a GW detector and the loudness of a GW source there are three commonly used quantities: the characteristic strain, the power spectral density, and the spectral energy density. Here we have carefully defined these quantities and derived the relationships between them. In addition example sensitivity curve plots using each of these quantities have been presented for a wide range of ground based detectors, space based detectors and pulsar timing arrays. Also plotted are predicted amplitudes for a wide range of sources, these predictions are based on astrophysical estimates of the event rates for a range of processes and are subject to varying degrees of uncertainty. There also exists the exciting possibility of sources nobody has yet considered. Interactive versions of these plots with user specified detectors and sources are made available on-line at \url{http://www.ast.cam.ac.uk/~rhc26/sources/}. Trying to summarise an entire field of astronomy on one plot is an impossible task; however we hope that the figures and analysis presented here provide useful insight.

>>>>

\documentclass[fleqn,12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
\usepackage{iopams}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{natbib}
\usepackage{appendix}
\usepackage[margin=1cm]{caption}
\usepackage{braket}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{color}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% 	definition of a solar mass symbol for use in equations.      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Msun}{\ensuremath{M_{ \odot }}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\innerprod}[2]{\ensuremath{\left({#1}\middle|{#2}\right)}}
\newcommand{\cplb}[1]{{\color{red} #1}}
\newcommand{\rhc}[1]{{\color{green} #1}}
\newcommand{\cjm}[1]{{\color{blue} #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Concluding remarks}\label{sec:discussion}

When quantifying the sensitivity of a GW detector and the loudness of a GW source, there are three commonly used quantities: the characteristic strain, the power spectral density, and the spectral energy density. We have carefully defined these quantities and derived the relationships between them. The characteristic strain (section \ref{sec:character-strain}) is most directly related to the SNR, the power spectral density is mostly closely related to the mean square amplitude in the detector, and the energy density has a clear physical interpretation. We have produced example plots using each of these quantities for a wide range of detectors and sources. The predicted source amplitudes are based on astrophysical estimates of the event rates and are subject to varying degrees of uncertainty.\footnote{There is also the exciting possibility of sources yet to be considered.} Interactive versions of these plots, with user-specified detectors and sources, are available on-line at \url{http://www.ast.cam.ac.uk/~rhc26/sources/}. Trying to summarise an entire field of astronomy on one plot is an impossible task; however, we hope that the figures and analysis presented here provide useful insight.
